WORKING TITLE: The adaptive value of green nest material across birds: A systematic review and meta-analysis

### 2025-02-17 manuscript_GNM.qmd
Added supplementary material and a structure that should work in principle

We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024]. We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1). All resources associated with this study, including data and code, are available at [https://github.com/shreyadimri/Green_Nest_Material](#0){.uri} (insert Zenodo citation later).

@@

#### Eligibility criteria

@@

# Supplementary Materials

<details><summary> Supplementary materials </summary>
{{< include supplementary_appendix.qmd >}}
</details>

>>>>

We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024]. We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1). All resources associated with this study, including data and code, are available at <https://github.com/shreyadimri/Green_Nest_Material> (insert Zenodo citation later).

@@

#### ility criteria

@@

<details>

<summary>Supplementary Appendix</summary>

{{< include supplementary_appendix.qmd >}}

</details>
